### 2023-06-23 bachelorthesis/04-declaration.tex
#39: Link to Repository in Declaration

The author declares that the materials presented in this thesis are his own work, unless explicitly stated otherwise. This thesis is based on
\bigskip
\begin{itemize}
    \item [] \bibentry{Lippert2023}
\end{itemize}
\bigskip
and is a further iteration of this publication (brief communication). It provides additional plots and paragraphs that were included in the publication. The brief communication can be found in Appendix \ref{append:paper}.

>>>>

The author declares that the materials presented in this thesis are his own work, unless explicitly stated otherwise. This thesis is based on
\bigskip
\begin{itemize}
    \item [] \bibentry{Lippert2023}
\end{itemize}
\bigskip
and is a further iteration of this publication (brief communication). It provides additional plots and paragraphs that were included in the publication. The brief communication can be found in Appendix \ref{append:paper}.\bigskip

Additionally, the author states that every information, except data, regarding this thesis can be found under the GitHub Repository with the link \url{https://github.com/ManeLippert/Bachelorthesis-Shearingrate-Convergence}.
